\section{Discussion}
\label{sec:discussion}

\paragraph{No single defense dominates.}
Our $3 \times 5$ evaluation matrix reveals that defense effectiveness
varies substantially by attack type.  Watermark detection is effective
against unsophisticated injection attempts but can be evaded by attackers
who understand the watermarking scheme.  \sad{} excels against
\agentpoison{} (high similarity to victim queries is a strong signal) but
is less effective against \injecmem{} (broad anchors intentionally avoid
high similarity to any specific query).  Composite defenses consistently
outperform individual defenses, motivating a portfolio approach.

\paragraph{Trigger prepending is a fundamental protocol requirement.}
The evaluation correction identified in Section~\ref{sec:experiments}
is not merely an implementation artifact.  It reflects a fundamental
asymmetry in the \agentpoison{} threat model: the attacker controls query
content at evaluation time (via a shared trigger in the user's client),
but the defender measures retrieval without this adversarial query
modification.  Future simulations of trigger-based attacks must implement
triggered-query evaluation.

\paragraph{Centroid passage approximation.}
Our centroid-targeting passage (Eq.~\ref{eq:centroid}) is a practical
approximation of the optimal adversarial passage that would require full
DPR-based gradient optimization.  At $\asrr=1.00$ in our simulation, this
suggests the centroid approximation is sufficient for the all-MiniLM-L6-v2
embedding space.  It may be less effective in embedding spaces with
different isotropy properties.

\paragraph{Limitations.}
(i) $\asra$ is modelled rather than measured from live agent execution,
which would require running production LLM agents across thousands of
evaluation queries.  (ii) The character-level watermark is weaker than
the token-level scheme of \citet{zhao2024watermark}; real-world deployment
would use an LLM backbone for token-level embedding.  (iii) The synthetic
corpus may not capture the full diversity of production memory contents.

\paragraph{Future work.}
Key extensions include: GPU-accelerated DPR-based trigger optimization;
live agent integration for true $\asra$ measurement; token-level watermark
for full paper-fidelity comparison; multi-agent propagation experiments
(poison that spreads across agents sharing a knowledge base); and
adaptive adversaries that optimize specifically to evade \sad{}.
