\section{Threat Model}
\label{sec:threat}

\paragraph{System model.}
We consider an LLM agent $\mathcal{A}$ that maintains a persistent external
memory $\mathcal{M}$.  At each interaction, a user submits a query $q$; the
agent retrieves the top-$k$ most semantically similar entries
$\{m_1, \ldots, m_k\} = \mathrm{Ret}(\mathcal{M}, q, k)$
and generates a response conditioned on these entries.  Memory entries are
stored as dense vectors $E(m) \in \RR^d$ using an embedding model $E$
(e.g., all-MiniLM-L6-v2, $d=384$).  Retrieval uses cosine similarity:
\begin{equation}
  \mathrm{Ret}(\mathcal{M}, q, k) = \arg\mathrm{top}\text{-}k_{m \in \mathcal{M}}\;
  \frac{E(q)^\top E(m)}{\|E(q)\| \|E(m)\|}.
  \label{eq:retrieval}
\end{equation}

\paragraph{Attacker goal.}
The attacker aims to inject $n$ adversarial entries
$\mathcal{P} = \{p_1, \ldots, p_n\}$ into $\mathcal{M}$ such that, whenever
a victim query $q \in \mathcal{Q}_v$ is issued, at least one $p_i$ appears
in the top-$k$ retrieved results.  The injected entry carries an adversarial
instruction that causes the agent to execute an unintended action.

\paragraph{Success metrics.}
Following \citet{chen2024agentpoison}:
\begin{align}
  \asrr &= \frac{|\{q \in \mathcal{Q}_v : \mathcal{P} \cap \mathrm{Ret}(\mathcal{M}, q, k) \neq \emptyset\}|}{|\mathcal{Q}_v|}, \label{eq:asrr} \\
  \asra &= \Pr[\text{agent executes adversarial action} \mid \text{poison retrieved}], \label{eq:asra} \\
  \asrt &= \asrr \times \asra. \label{eq:asrt}
\end{align}
$\asra$ is modelled from paper-reported values since it requires live agent
execution (Section~\ref{sec:attacks}).

\paragraph{Attacker capabilities (three threat models).}
\begin{description}
  \item[\agentpoison{}] \emph{Full write access}: attacker can directly
  insert entries into $\mathcal{M}$.  Attacker knows the embedding model $E$
  and can optimize a trigger token sequence $\trigger$.  Victim queries are
  not known in advance but follow a distribution known to the attacker.

  \item[\minja{}] \emph{Query-only}: attacker can only submit queries to the
  agent.  No direct memory access.  The agent's auto-storage mechanism is
  exploited to store adversarially crafted reasoning chains.

  \item[\injecmem{}] \emph{Single-interaction}: attacker submits one crafted
  interaction.  No trigger token; attack relies on a broad-coverage anchor
  passage.
\end{description}

\paragraph{Benign accuracy.}
We additionally measure the fraction of off-target (benign) queries that do
\emph{not} retrieve any adversarial entry.  A stealthy attack preserves high
benign accuracy while achieving high $\asrr$ on victim queries.
