% Memory Agent Security: Unified Attack Evaluation and Defense Framework
% Target: NeurIPS 2026 or ACM CCS 2026
%
% Compilation: pdflatex main.tex && bibtex main && pdflatex main.tex && pdflatex main.tex
% Or use latexmk: latexmk -pdf main.tex

\documentclass[10pt]{article}

% --- packages ---
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{subcaption}
\usepackage{microtype}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, shapes.geometric, fit, backgrounds, patterns}

% --- figure path (all generated figures live in figures/) ---
\graphicspath{{figures/}}

% --- theorem environments ---
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

% --- custom macros ---
\newcommand{\asrr}{\text{ASR-R}}
\newcommand{\asra}{\text{ASR-A}}
\newcommand{\asrt}{\text{ASR-T}}
\newcommand{\isr}{\text{ISR}}
\newcommand{\tpr}{\text{TPR}}
\newcommand{\fpr}{\text{FPR}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\sad}{\textsc{SAD}}
\newcommand{\agentpoison}{\textsc{AgentPoison}}
\newcommand{\minja}{\textsc{MINJA}}
\newcommand{\injecmem}{\textsc{InjecMEM}}
\newcommand{\trigger}{T}
\newcommand{\passage}{p_{\mathrm{adv}}}
\newcommand{\enc}{E}

\title{%
  \textbf{Poisoning the Memory: A Unified Framework for Attacking and\\
  Defending LLM Agent Memory Systems}
}

\author{%
  Ishrith Gowda\\
  University of California, Berkeley\\
  \texttt{ishrithgowda@berkeley.edu}
}

\date{Draft --- \today}

\begin{document}

\maketitle

\begin{abstract}
LLM agents increasingly rely on external memory systems to persist context
across sessions.  We show that this memory constitutes a critical and largely
undefended attack surface.  We present a unified evaluation framework for
three recently proposed memory poisoning attacks---\agentpoison{}
\citep{chen2024agentpoison}, \minja{} \citep{dong2025minja}, and
\injecmem{} \citep{injecmem2026}---implemented over a realistic FAISS-backed
vector memory store (all-MiniLM-L6-v2, 384-dim) with a 200-entry synthetic
agent memory corpus.

We identify and correct a systematic evaluation error in prior simulations:
\agentpoison{}'s attack success rate at retrieval (\asrr) was underestimated
because victim queries were issued \emph{without} the attacker-controlled
trigger token at evaluation time.  The paper's evaluation protocol
(Chen et al., Algorithm~2) prepends the trigger to every query;
with this correction and a centroid-targeting adversarial passage,
\asrr{} increases from 0.25 to 1.00 at 2.4\% poison rate.

On the defense side, we propose \sad{}---a Semantic Anomaly Detection
defense that flags adversarial memory entries by their anomalously high
cosine similarity to observed victim queries.  We evaluate all five defenses
(Watermark, Validation, Proactive, Composite, \sad{}) in a pre-ingestion
filtering model across a full $3 \times 5$ attack-defense interaction matrix.
We find that no single defense is uniformly effective, motivating composite
defense portfolios.  For \sad{} specifically, we prove and empirically confirm
a fundamental tension for white-box adaptive adversaries: any synonym
substitution that reduces the anomaly score also reduces the adversarial
passage's retrieval rank, because both objectives share the same cosine
similarity gradient.  This structural property limits the adaptive adversary
to at most 60\% evasion rate, with a corresponding $\geq 0.40$ drop in
ASR-R, confirming \sad{}'s robustness under adaptive attack.

All code, experiments, and figures are open-sourced at
\url{https://github.com/ishrith-gowda/memory-agent-security}.
\end{abstract}

% section files
\input{sections/introduction}
\input{sections/related_work}
\input{sections/threat_model}
\input{sections/attacks}
\input{sections/defenses}
\input{sections/experiments}
\input{sections/discussion}
\input{sections/conclusion}

\bibliography{references}
\bibliographystyle{plainnat}

\appendix
\input{sections/appendix}

\end{document}
